\documentclass[10pt,a4paper]{article}
\usepackage[a4paper,top=2cm, left=1.5cm, right=1.5cm, bottom=1.5cm]{geometry}
\usepackage{resume}
\usepackage[english]{babel}
\usepackage{lato}
\usepackage{fontawesome5}
\usepackage{academicons}
\hyphenation{super-vision}
\frenchspacing


\begin{document}
\sloppy

\maintitle{\huge{Soumadeep Saha}}{\\Senior Research Fellow, \textbf{Indian Statistical Institute, Kolkata}}{}

\nobreakvspace{0.3em}
\noindent
\href{mailto:soumadeep.saha\_r@isical.ac.in}{\faEnvelope[regular] soumadeep.saha\_r@isical.ac.in}\sbull
\href{mailto:soumadeep.saha97@gmail.com}{\faEnvelope[regular] soumadeep.saha97@gmail.com}\sbull
\href{tel:+918697373806}{\faPhone (\textsmaller{+}91) 869 737 3806}\sbull
\href{https://github.com/espressovi}{\faGithub[regular]}\sbull
\href{https://www.linkedin.com/in/soumadeep-saha-a36a58103/}{\faLinkedin[regular]}\sbull
\href{https://espressovi.github.io}{\faLink}
\spacedhrule{0.6em}{-0.7em}
%--------------------------------- COVER ---------------------------------------
\roottitle{Summary}
\vspace{-0.2em}
    I am a \emph{senior research fellow} at
    \href{https://www.isical.ac.in/}{ISI Kolkata}, working under the
    supervision of \href{https://www.isical.ac.in/~utpal}{Prof. Utpal Garain}.
    My research centers on enhancing deep learning systems with the strengths of
    symbolic AI techniques for greater logical coherence and domain constraint
    adherence. While my primary focus is natural language processing, I actively
    collaborate across domains including vision, medicine, biology,
    astrophysics, and business applications.   

    My doctoral dissertation titled ``\textbf{Domain Obedient Deep Learning}''
    is \emph{under review}. My ongoing research focusing on alignment of large
    language models has recently been supported by an \emph{OpenAI Computational
    Credit Grant}.

\spacedhrule{1em}{-0.7em}

%--------------------------------- EDUCATION -----------------------------------
\roottitle{Education}

\headedsection{\href{http://www.iiserkol.ac.in}{Indian Institute of Science Education and Research, Kolkata}}
    {\textsc{Kolkata, India}}{
        \headedsubsection{Integrated BS \& MS in Physics (Minor in Mathematics)}{2015--2020}{
            \bodytext{
                \begin{itemize}
                    \item[\ding{111}] Awarded the Kishore Vigyan Pratoshan Yojna
                        (\textbf{KVPY}) fellowship from the Department of
                        Science and Technology, Govt. of India (GoI).
                    \item[\ding{111}] Master's dissertation:
                        \textbf{\href{https://espressovi.github.io/pdf/MastersThesis.pdf}{``Towards Robust Deep Learning Systems''}}.
                \end{itemize}
            }
        }
}
\headedsection{\href{https://bhavansgkvidyamandir.edu.in/}{Bhavan's G.K. Vidyamandir}}
    {\textsc{Kolkata, India}}{
        \headedsubsection{10+2 \textnormal{~(Pre-University Secondary Education)}}{2002--2015}{
            \bodytext{
                \begin{itemize}
                    \item[\ding{111}] Recipient of the prestigious National Talent Search Examination (\textbf{NTSE}) Scholarship from NCERT, GoI.
                    \item[\ding{111}] CBSE (10th standard): $91.2\%$; AISSCE (12th standard): $92\%$.
                \end{itemize}
        }
    }
}
\spacedhrule{1em}{-0.7em}

%--------------------------------- PUBLICATIONS --------------------------------
\roottitle{Publications \href{https://scholar.google.com/citations?user=RMegz-MAAAAJ&hl=en}{\aiGoogleScholar}}

\headedsection{\ding{111} \href{https://aclanthology.org/2025.naacl-long.104/}{Language Models are Crossword Solvers}}
    {\textbf{NAACL 2025} (main)}
    {\headedsubsection{\textbf{S. Saha}, \normalfont{S. Chakraborty, S. Saha, U. Garain}}{}{} }
\vspace{0.4em}

\headedsection{\ding{111} \href{https://arxiv.org/pdf/2505.09660}{On Measuring Intrinsic Causal Attributions in Deep Neural Networks}}
    {\textbf{CLeaR 2025}}
    {\headedsubsection{\normalfont{S. Saha, D. V. Rathore, \textbf{S. Saha}, D. Doermann, U. Garain.}}{}{Accepted Jan. 2025} }
\vspace{0.4em}

\headedsection{\ding{111} \href{https://direct.mit.edu/coli/article/50/1/119/118135/Analyzing-Semantic-Faithfulness-of-Language-Models}{Analyzing Semantic Faithfulness of Language Models via Input Intervention on\\ Conversational Question Answering}}
    {\textbf{Computational Linguistics} (2024), 50(1): 119-155}
    {\headedsubsection{\normalfont{A. Chaturvedi, S. Bhar, \textbf{S. Saha}, U. Garain, N. Asher}}{}{} }
\vspace{0.4em}

\headedsection{\ding{111} \href{https://data.mlr.press/assets/pdf/v01-13.pdf}{VALUED - Vision and Logical Understanding Evaluation Dataset}}
    {\textbf{DMLR} (2024), (13):1-18.}
    {\headedsubsection{\normalfont{\textbf{S. Saha}, S. Saha, U. Garain}} {}{} }
\vspace{0.4em}

\headedsection{\ding{111} \href{https://doi.org/10.1371/journal.pone.0283895}{MedTric : A clinically applicable metric for evaluation of multi-label computational\\ diagnostic systems}}
    {\textbf{PLOS One} (2023), 18(8): e0283895}
    {\headedsubsection{\normalfont{\textbf{S. Saha}, U. Garain, A. Ukil, A. Pal, S. Khandelwal.}}{}{} }
\vspace{0.4em}

\headedsection{\ding{111} \href{https://link.springer.com/chapter/10.1007/978-3-031-63592-2_10}{DOST -- Domain Obedient Self-supervised Training for Multi Label Classification\\ with Noisy Labels}}
    {\textbf{AAAI 2024 Workshop (W3PHIAI)} (2024), 1164: 117-127}
    {\headedsubsection{\normalfont{\textbf{S. Saha}, U. Garain, A. Ukil, A. Pal, S. Khandelwal.}}{}{} }
\vspace{0.4em}

\headedsection{\ding{111} \href{https://iopscience.iop.org/article/10.3847/1538-4365/ad5558}{LADDER: Revisiting the Cosmic Distance Ladder with Deep Learning Approaches\\ and Exploring its Applications}}
    {\textbf{APJS} (2024), 273(2): 27}
    {\headedsubsection{\normalfont{R. Shah, \textbf{S. Saha}, P. Mukherjee, U. Garain, S. Pal}}{}{} }
\vspace{0.4em}

\headedsection{\ding{111} \href{https://arxiv.org/abs/2412.14750}{Deep Learning Based Recalibration of SDSS and DESI BAO Alleviates Hubble\\ and Clustering Tensions}}
    {Preprint. 10.48550/arXiv.2412.14750} 
    {\headedsubsection{\normalfont{R. Shah, P. Mukherjee, \textbf{S. Saha}, U. Garain, S. Pal}}{}{Under review at APJL.}}
\spacedhrule{1em}{-0.7em}

%--------------------------------- PATENTS -------------------------------------
\roottitle{Patents}

\headedsection{\ding{111} \href{https://patents.google.com/patent/US12038949B2/en}{Method and System for Contradiction Avoided Learning for Multi-Class\\Multi-Label Classification}}
    {\textbf{US Patent - US12038949B2}}
    {\headedsubsection{\normalfont{\textbf{S. Saha}, U. Garain, A. Ukil, A.Pal}}{}{Granted Jul. 2024}}
\vspace{0.4em}

\headedsection{\ding{111} \href{https://patents.google.com/patent/US20240096492A1/en}{Method and System for Evaluating Clinical Efficiency of Multi-Label Multi-Class Computational\\Diagnostic Models}}
    {\emph{Pending}}
    {\headedsubsection{\normalfont{U. Garain, \textbf{S. Saha}, A. Ukil, T. Deb, S. Richa A. Pal, S. Khandelwal}}{}{Filed Sep. 2022.}}
\spacedhrule{1em}{-0.4em}

\newpage
\spacedhrule{0em}{-0.7em}
%--------------------------------- EXPERIENCE ----------------------------------
\roottitle{Experience}

\headedsection{\textbf{Helmholtz Visiting Researcher}}{Jul \apo24--Sep \apo24}{
    \bodytext{
        Awarded the Helmholtz Information and Data Science Academy (HIDA)
        visiting researcher grant to work at the Institute of Aerospace
        Medicine, DLR (German Aerospace Center). Conducted research on improving
        AI-based retinal diagnostics for spaceflight applications.
    }
}

\headedsection{\textbf{Alleima}}{Mar \apo24--May \apo24}{
    \bodytext{
        Developed a custom end-to-end computer vision-based solution for
        assembly-line object detection/tracking, enabling autonomous logging of
        crucial data with existing infrastructure.
    }
}

\headedsection{\textbf{TCS Research}}{Nov \apo21 -- Jul \apo22}{
    \bodytext{
        Conducted research as part of a team on ECG-based diagnosis of
        cardiovascular diseases. Independently identified key gaps in the
        literature and developed innovative, state-of-the-art solutions to
        address them, resulting in two patents, and publications.
    }
}

%\headedsection{\textbf{Deep Analysis of Pain Management}}{Jun \apo20 -- Nov \apo20}{
%    \bodytext{
%        Collaborated with medical professionals in the field of radiodiagnosis
%        to formulate a problem statement and set up data-gathering protocols to
%        create a high-quality data set for the analysis of back pain from MRI
%        images.
%    }
%}

\headedsection{\textbf{Talks and Presentations}}{}{
    \bodytext{
        \begin{itemize}
            \item[\ding{111}] Organized a 4-day workshop for DataLab, \textbf{Capital One}, Bangalore (2023).
            \item[\ding{111}] Subject matter expert for Be10x--delivered video tutorials and live classes to 500+ participants (2024).
            \item[\ding{111}] TA for Natural Language Processing course at ISI Kolkata (2022, 2023, 2024).
            \item[\ding{111}] Instructor at the Winter School of Deep Learning (WSDL), ISI Kolkata (2021, 2022, 2023, 2024).
            \item[\ding{111}] Instructor for the Comprehensive Course on Business Analytics, ISI Kolkata (2022).
            \item[\ding{111}] Presented my work on Logically Coherent Deep Learning at Amazon Research Days (ARD \apo22).
            \item[\ding{111}] Presented my work on domain-obedient self-supervision at W3PHIAI, 38th AAAI Conference, Vancouver, Canada (AAAI \apo24).
        \end{itemize}
    }
}

\spacedhrule{1em}{-0.4em}

%--------------------------------- SKILLS --------------------------------------
\roottitle{Skills}

 \ding{111} \textbf{Deep Learning}: Expert in deep learning theory and practice, from low-level optimization to advanced architectures and training paradigms.\\
 \ding{111} \textbf{Programming}: \textbf{Python} (\textbf{\texttt{pytorch}}, \texttt{nympy}, etc.), C++, FORTRAN, bash, etc.\\
 \ding{111} \textbf{NLP}: Significant LLM expertise (in-context learning, RAG, PEFT, Q-LoRA, instruction tuning, RLHF, DPO, etc.)\\
 \ding{111} \textbf{Vision}: Vision transformers, CNNs, VLMs, object detection, segmentation, etc.\\
 \ding{111} \textbf{Deep RL}: DQN, PPO, MCTS, etc. \\

\spacedhrule{1em}{-0.4em}

%--------------------------------- INTERESTS -----------------------------------
\roottitle{Interests}

	 \ding{111} \textbf{Robotics/DIY}--Active interest in 3D printing,
     robotics, electronics, etc. I have conducted introductory workshops on
     robotics and was the Secretary of the Robotics and Astronomy Club at IISER
     Kolkata.\\
	 \ding{111} \textbf{Sports}--Represented my college in national-level sports
     meets in basketball and volleyball. Played in my state's Senior Division
     Men's Basketball League.\\
	 \ding{111} \textbf{Music}--Classically trained pianist.\\

\spacedhrule{1em}{-0.4em}

\end{document}
